------------------------------------------------------------------------

```{r}
#first library a few packages that we will use during the practical
#note you may need to install them first...
install.packages('spatstat')
library(spatstat)
library(here)
library(sp)
library(rgeos)
library(maptools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)
```
```{r}
##First, get the London Borough Boundaries
LondonBoroughs <- st_read(here::here("Data", "statistical-gis-boundaries-london", "ESRI", "London_Borough_Excluding_MHW.shp"))
LondonBoroughs
```

```{r}
#use this to read in directly.
#LondonBoroughs <- st_read("https://opendata.arcgis.com/datasets/8edafbe3276d4b56aec60991cbddda50_4.geojson")
```
```{r}
##filter code of London and standardize crs
library(stringr)
BoroughMap <- LondonBoroughs %>%
  dplyr::filter(str_detect(GSS_CODE, "^E09"))%>%
  st_transform(., 27700)

qtm(BoroughMap)
summary(BoroughMap)
```

##Now get the location of all Blue Plaques in the City
```{r}

BluePlaques <- st_read("https://s3.eu-west-2.amazonaws.com/openplaques/open-plaques-london-2018-04-08.geojson")%>%
  st_transform(.,27700)

summary(BluePlaques)
```
#plot the blue plaques in the city
```{r}

tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaques) +
  tm_dots(col = "blue")
```
#remove duplicates rows
```{r}

library(tidyverse)

library(sf)
BluePlaques <- distinct(BluePlaques)
```


###clip data by boroughmap
```{r}
BluePlaquesSub <- BluePlaques[BoroughMap,]
###he second operator is blank , , - this controls which attributes are kept
#裁剪数据
###或者intersect_indices <-st_intersects(BoroughMap, BluePlaques)
tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaquesSub) +
  tm_dots(col = "blue")
```
##???why can't plot?what data type is indices?
```{r}
intersect_indices <-st_intersects(BoroughMap, BluePlaques)
tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(intersect_indices) +
  tm_dots(col = "blue")
```
#extract the borough
```{r}


# select by attribute
Harrow <- BoroughMap %>%
  filter(., NAME=="Harrow")

#Check to see that the correct borough has been pulled out
tm_shape(Harrow) +
  tm_polygons(col = NA, alpha = 0.5)
```
##clip data to a borough
##??st_intersect output what?
```{r}
BluePlaquesSub <- st_transform(BluePlaquesSub,27700)
LondonBoroughs <- st_transform(LondonBoroughs,27700)
BluePlaquesSub1 <- st_intersects(LondonBoroughs,BluePlaquesSub)
BluePlaquesSub2 <- BluePlaquesSub[Harrow,]
```


```{r}
tmap_mode=("plot")
tm_shape(Harrow)+
  tm_polygons(col=NA,alpha=0.5)+
tm_shape(BluePlaquesSub2)+
  tm_dots(col="blue",size=0.05)
```
#now set an observation window as the borough boundary
```{r}

window <- as.owin(Harrow)
plot(window)
```

#create a sp object
```{r}

BluePlaquesSub<- BluePlaquesSub2 %>%
  as(., 'Spatial')
#create a ppp object
BluePlaquesSub.ppp <- ppp(x=BluePlaquesSub@coords[,1],
                          y=BluePlaquesSub@coords[,2],
                          window=window)
BluePlaquesSub.ppp %>%
  plot(.,pch=16,cex=0.5, 
       main="Blue Plaques Harrow")
```
#try
```{r}
BluePlaquesSub@coords[,1]
```
##Kernel Density Estimation核密度
```{r}
BluePlaquesSub.ppp %>%
  density(., sigma=500) %>%
  plot()
###sigma is diameter
```

```{r}
#First plot the points
plot(BluePlaquesSub.ppp,
     pch=16,
     cex=0.5, 
     main="Blue Plaques in Harrow")

#now count the points in that fall in a 6 x 6
#grid overlaid across the windowBluePlaquesSub.ppp2<-BluePlaquesSub.ppp %>%
BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6)%>%
    plot(., add=T, col="red")
```

```{r}
#run the quadrat count
Qcount <- BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6) %>%
  as.data.frame() %>%
  dplyr::count(Var1=Freq)%>% ###group by freq and count
  dplyr::rename(Freqquadratcount=n)
Qcount %>% 
  summarise_all(class)
```

```{r}
Qcount1 <- BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6) %>%
  as.data.frame()
```

```{r}
sums <- Qcount %>%
  #calculate the total blue plaques (Var * Freq)
  mutate(total = Var1 * Freqquadratcount) %>%
  dplyr::summarise(across(everything(), sum))%>%
  dplyr::select(-Var1) 

lambda <- Qcount %>%
  mutate(total = Var1 * Freqquadratcount) %>%  ## 计算每个样本的Var1和Freqquadratcount的乘积，并创建新列total
  dplyr::summarise(across(everything(), sum)) %>%  ## 对所有列求和，每列变成其所有值的总和
  mutate(lambda = total / Freqquadratcount) %>%  ## 使用总和total除以Freqquadratcount列的值来计算lambda
  dplyr::select(lambda) %>%  ## 选择lambda列
  pull(lambda)  ## 将lambda列的值提取出来，转换成一个向量
```

```{r}
QCountTable <- Qcount %>%
  mutate(Pr=((lambda^Var1)*exp(-lambda))/factorial(Var1)) %>%  ## 根据泊松分布计算Var1出现的概率Pr
  mutate(Expected= (round(Pr * sums$Freqquadratcount, 0)))  ## 计算预期计数并四舍五入到最接近的整数

# 对观测点模式和预期点模式的频率分布进行比较
plot(c(1,5),c(0,14), type="n",  ## 初始化一个空图形，设置x轴和y轴的范围
xlab="Number of Blue Plaques (Red=Observed,Blue=Expected)",  ## 设置x轴标签
     ylab="Frequency of Occurances")  ## 设置y轴标签
points(QCountTable$Freqquadratcount,  ## 添加观测频率数据点（红色）
       col="Red", 
       type="o", 
       lwd=3)
points(QCountTable$Expected, col="Blue",  ## 添加预期频率数据点（蓝色）
       type="o", 
       lwd=3)
```

```{r}
teststats <- quadrat.test(BluePlaquesSub.ppp, nx = 6, ny = 6)
```

```{r}
plot(BluePlaquesSub.ppp,pch=16,cex=0.5, main="Blue Plaques in Harrow")
plot(teststats, add=T, col = "red")
```
#conduct a Ripley’s K test on our data very simply with the spatstat package using the kest() function.
#to
```{r}
K <- BluePlaquesSub.ppp %>%
  Kest(., correction="border") %>%
  plot()
Kval <- as.data.frame(Kest(BluePlaquesSub.ppp, correction = "Ripley"))
##当K大于小于实际值，说明在一定半径内相对集中
```
###DBSCAN
```{r}
##DBSCAN 要求您输入两个参数：1. Epsilon - 这是算法搜索聚类的半径 2.MinPts - 这是应被视为群集的最小点数

#
##根据前面的 Ripley K 分析结果，我们可以看到，我们的聚类半径约为 1200 米，图中最大的凸起位于 700 米左右。因此，700m 可能是一个很好的起点，我们将从搜索至少 4 个点的集群开始......
install.packages('fpc')
library(raster)
library(fpc)
#first check the coordinate reference system of the Harrow spatial polygon:
st_geometry(BoroughMap)
```

```{r}
#first extract the points from the spatial points data frame
BluePlaquesSubPoints <- BluePlaquesSub %>%
  coordinates(.) %>%
  as.data.frame()  ## 从空间数据框 BluePlaquesSub 提取坐标并转换成数据框

#now run the dbscan analysis
db <- BluePlaquesSubPoints %>%
  fpc::dbscan(.,eps = 700, MinPts = 4)

#now plot the results
plot(db, BluePlaquesSubPoints, main = "DBSCAN Output", frame = F)
plot(BoroughMap$geometry, add=T)
```
??
```{r}
# used to find suitable eps value based on the knee in plot
# k is no of nearest neighbours used, use min points
install.packages('dbscan')
library(dbscan)

BluePlaquesSubPoints%>%
  dbscan::kNNdistplot(.,k=4)
##Next, these k-distances are plotted in an ascending order. The aim is to determine the “knee”, which corresponds to the optimal eps parameter.
#接下来，按升序绘制这些 k 距离。目的是确定“拐点”，它对应于最佳 eps 参数。

#A knee corresponds to a threshold where a sharp change occurs along the k-distance curve.
#拐点对应于沿 k 距离曲线发生急剧变化的阈值。
```
#plot
```{r}
BluePlaquesSubPoints <- BluePlaquesSubPoints %>%
  mutate(dbcluster=db$cluster)  ## 将DBSCAN聚类结果添加到数据框中

chulls <- BluePlaquesSubPoints %>%
  group_by(dbcluster) %>%
  dplyr::mutate(hull = 1:n()) %>%
  dplyr::mutate(hull = factor(hull, chull(coords.x1, coords.x2))) %>%
  arrange(hull)  ## 对每个聚类计算凸包，并将其作为因子类型的新列添加到数据框中

# chulls2 <- ddply(BluePlaquesSubPoints, .(dbcluster), 
#                  function(df) df[chull(df$coords.x1, df$coords.x2), ])
## 上述被注释的代码是另一种计算凸包的方法，使用了plyr包的ddply函数

chulls <- chulls %>%
  filter(dbcluster >= 1)  ## 从数据中过滤掉噪声点，即那些不属于任何聚类的点（通常dbcluster标记为0或-1）

dbplot <- ggplot(data = BluePlaquesSubPoints, 
                 aes(coords.x1, coords.x2, colour = dbcluster, fill = dbcluster))  ## 初始化ggplot对象，并设置绘图的美学属性

# 添加点到图中
dbplot <- dbplot + geom_point()  ## 使用geom_point添加散点图层

# 现在添加凸包
dbplot <- dbplot + geom_polygon(data = chulls, 
                                aes(coords.x1, coords.x2, group = dbcluster), 
                                alpha = 0.5)  ## 使用geom_polygon添加凸包图层，透明度设为0.5以便观察点

# 最后绘制图形，设置坐标比例一致，并使用黑白主题
dbplot + theme_bw() + coord_equal()  ## 应用黑白主题，并确保x和y轴具有相同的比例
###add a basemap
##First get the bbox in lat long for Harrow
HarrowWGSbb <- Harrow %>%
  st_transform(., 4326)%>%
  st_bbox()
library(OpenStreetMap)

basemap <- OpenStreetMap::openmap(c(51.5549876,-0.4040502),c(51.6405356,-0.2671315),
                         zoom=NULL,
                         "osm")

  # convert the basemap to British National Grid
basemap_bng <- openproj(basemap, projection="+init=epsg:27700")
#autoplot(basemap_bng) sometimes works
autoplot.OpenStreetMap(basemap_bng)+ 
  geom_point(data=BluePlaquesSubPoints, 
             aes(coords.x1,coords.x2, 
                 colour=dbcluster, 
                 fill=dbcluster)) + 
  geom_polygon(data = chulls, 
               aes(coords.x1,coords.x2, 
                   group=dbcluster,
                   fill=dbcluster), 
               alpha = 0.5)  
```

